Customize the format of rcell

### 2023-04-16 posts/rtables/customize_cell.qmd
fix typo

```{r rcell1}
#| echo: true
#| eval: false
rcell(
x,
format = NULL,
colspan = 1L,
rcell 103
label = NULL,
indent_mod = NULL,
footnotes = NULL,
align = NULL,
format_na_str = NULL
)
```

>>>>

```{r rcell1}
#| echo: true
#| eval: false
rcell(
x,
format = NULL,
colspan = 1L,
label = NULL,
indent_mod = NULL,
footnotes = NULL,
align = NULL,
format_na_str = NULL
)
```
